\documentclass[a4paper]{scrreprt}

% Uncomment to optimize for double-sided printing.
% \KOMAoptions{twoside}

% Set binding correction manually, if known.
% \KOMAoptions{BCOR=2cm}

% Localization options
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% Quotations
\usepackage{dirtytalk}

% Floats
\usepackage{float}

% Enhanced verbatim sections. We're mainly interested in
% \verbatiminput though.
\usepackage{verbatim}

% Automatically remove leading whitespace in lstlisting
\usepackage{lstautogobble}

% PDF-compatible landscape mode.
% Makes PDF viewers show the page rotated by 90°.
\usepackage{pdflscape}

% Advanced tables
\usepackage{array}
\usepackage{tabularx}
\usepackage{longtable}

% Fancy tablerules
\usepackage{booktabs}

% Graphics
\usepackage{graphicx}

% Current time
\usepackage[useregional=numeric]{datetime2}

% Float barriers.
% Automatically add a FloatBarrier to each \section
\usepackage[section]{placeins}

% Custom header and footer
\usepackage{fancyhdr}

\usepackage{geometry}
\usepackage{layout}

% Math tools
\usepackage{mathtools}
% Math symbols
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{amsthm}
% General symbols
\usepackage{stmaryrd}

% Utilities for quotations
\usepackage{csquotes}

% Bibliography
\usepackage[
  style=alphabetic,
  backend=biber, % Default backend, just listed for completness
  sorting=ynt % Sort by year, name, title
]{biblatex}
\addbibresource{references.bib}

\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

% Bullet point
\newcommand{\tabitem}{~~\llap{\textbullet}~~}

\pagestyle{plain}
% \fancyhf{}
% \lhead{}
% \lfoot{}
% \rfoot{}
% 
% Source code & highlighting
\usepackage{listings}

% SI units
\usepackage[binary-units=true]{siunitx}
\DeclareSIUnit\cycles{cycles}

\newcommand{\lecture}{41109 - Privacy and Data Security}
\newcommand{\series}{01}
% Convenience commands
\newcommand{\mailsubject}{\lecture - Series \series}
\newcommand{\maillink}[1]{\href{mailto:#1?subject=\mailsubject}
                               {#1}}

% Should use this command wherever the print date is mentioned.
\newcommand{\printdate}{\today}

\subject{\lecture}
\title{Series \series}

\author{Michael Senn \maillink{michael.senn@students.unibe.ch} - 16-126-880}

\date{\printdate}

% Needs to be the last command in the preamble, for one reason or
% another. 
\usepackage{hyperref}

\begin{document}
\maketitle


\setcounter{chapter}{\numexpr \series - 1 \relax}

\chapter{Series \series}

\section{Data vultures}

\subsection{Device tracking with ultrasonic beacons}

Ultrasonic beacons --- that is audio signals with frequencies above those which
can be heard by humans --- provide a way to track the presence of users'
devices. To do so, so-called `beacons' emit an ultrasound signal which is then
recorded by a device's microphone. When a device thus records such a signal it
knows that it is in proximity to the beacon emitting it, and can use this
information to e.g. deduce and report the user's approximate
location.\autocite{newmanHowBlockUltrasonic2016}

On the one hand this can be used to track a device's approximate location,
similar to how one might be able to do via the signed-in mobile-network cell,
or by tracking a device's wireless connections. More interestingly this allows
to e.g. correlate a person having heard an advertisement on TV, and later
visiting their local supermarket to buy the advertised product. This helps
answering the question of where and when a user was exposed to an advertisement
which made them buy the product.\autocite{fribergUltrasonicBeaconsSilent2017}

This technique's application however is limited in that it requires an
application with access to the device's microphone, reporting back to the
advertiser. It is likely that the permission for an application to access a
device's microphone is not granted lightly, which might well be one reason why
this technique has not found wider adoption.

\subsection{Inferring domestic activities using smart-meter based energy readings}

With the eventual goal of lowering energy consumption of domestic households,
smart meters have been introduced over the past few years. These provide an
aggregate energy usage of a household over the course of a day, both to the
inhabitants of the household as well as to the energy provider.

Research has shown that it is possible to combine such per-household power
usage data with statistical models about activities people engage in, to
determine which activity a household engaged in at a given
time.\autocite{stankovicMeasuringEnergyIntensity2016}.

This research was based on three components. Firstly there exist models,
stating which activities a demographic is likely to engage in at a given time.
Secondly certain activities involve appliances with typical usage patterns.
Consider a washing machine which will periodically draw a lot of power while
heating up water, while drawing noticeably less during other parts of the
washing cycle. Lastly, smart meters provide fine-grained energy usage
recordings on the time axis.

It was shown that certain activities could be inferred with high certainity
based on purely existing models, and a household's smart-meter-based power
recordings.\autocite{stankovicMeasuringEnergyIntensity2016}

The significance of these findings lies in that it is possible to learn about a
subset of a household's activities purely based on access to their power
consumption. Such access can be the result of unauthorized access, as smart
meters are historically insecure\autocite{starrYourSmartElectricity2017}, or of
data being passed from energy companies to third parties.

\subsection{Identifying people in `anonymous' datasets}

Often, large sets of data are made public in a way in which they are deemed
anonymous. Stripped of directly identifiable information such as name or
address, hospitals release data about procedures unertaken, fitness apps
release data about activities people engange in, or cab companies release tour
logs. \autocite{solonDataFingerprintWhy2018}

Research has shown however that, by combining this data with publically
available data such as voter registrations, newspaper articles, phone books or
public location information, a large percentage of entries in such datasets can
be identified. As an example, using a small number of purchases and rough
timestamps --- as one might gain from e.g. public social media posts ---
researchers were able to identify the person within millions of anonymised
credit card chargers, thereby exposing their whole purchasing
history. \autocite{demontjoyeUniqueShoppingMall2015}

This is likely to continue exposing a lot of information about people, as long
as companies keep mistakenly releasing information they deem anonymized.

\printbibliography

\end{document}

% - Identifying ppl in anonymized data sets (ref 61)
